Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-12 paper/tv.tex
m

\begin{wrapfigure}{L}{0.39\columnwidth}
  \vspace{-2mm}
\begin{lstlisting}
void addOneSugar() 
/*req: TRUE/\ _^*
  ens: t>1 /\ emp#t */ 
{ timeout ((), 1); }

@@

void process (int i)
/* req  d1<d2,  emp 
   ens  true, [x=-1](Update(i)#d1.emp#d2.
   ([x=i]Critical(i).Exit(i) \/ [x!=i]emp))^* */
{
  [x=-1] 
  deadline (event[Update(i)]{x := i}, d1);
  delay (d2);
  if (x=i) {
    event[Critical(i)]{ct := ct +1};
    event[Exit(i)]{ct := ct-1; x := -1};
    process (i);
  } else {
    process (i);
}

@@

\begin{figure}[ht]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
void addNSugar(int n)
/* req n>0,  _^*.Cup 
   ens  t>=n, Sugar # t */
{ if n == 0 then event[Sugar] 
  else {
    timeout ( addOneSugar(), 1);
    addNSugar (n-1);}}

void makeCoffee (int n)
/* req n>0, emp 
 ens  t<5/\t>=n/\t1<3, 
 Cup.(Sugar#t).(Coffee#t1).Done */
{ event[Cup];
  deadline (addNSugar(n), 5);
  deadline (event[Coffee], 3);
  event[Done];}

void main () 
/* req true, emp 
 ens  t<8, (_^*.Done)#t */
{ makeCoffee(3);}
// make coffee with 3 lumps of sugar

\end{lstlisting}  
      \vspace{0mm}
      \caption{Dependent Values for Time Bounds (the program is from  \cite{berry2020hiphop}).}\label{fig:overview_eg1}
         \vspace{0mm}
\end{figure}

@@

>>>>

\begin{wrapfigure}{L}{0.39\columnwidth}
  \vspace{-2mm}
\begin{lstlisting}
void addOneSugar() 
/*req: true/\ _^*
  ens: t>1 /\ emp#t */ 
{ timeout ((), 1); }

@@

@@

\begin{figure}[ht]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
void makeCoffee (int n)
/*req: n>0 /\ emp 
  ens: t<5/\t>=n/\t1<3 /\
Cup.(Sugar#t).(Coffee#t1).Done */
{ event[Cup];
  deadline (addNSugar(n), 5);
  deadline (event[Coffee], 3);
  event[Done];}

void main () 
/*req: true/\ emp 
  ens: t<8 /\ (_^*.Done)#t */
{ makeCoffee(3);}
// make coffee with 3 lumps of sugar
\end{lstlisting}  
      \vspace{0mm}
      \caption{Dependent Values for Time Bounds (the program is from  \cite{berry2020hiphop}).}\label{fig:overview_eg1}
         \vspace{0mm}
\end{figure}

@@

void process (int i)
/* req  d1<d2,  emp 
   ens  true, [x=-1](Update(i)#d1.emp#d2.
   ([x=i]Critical(i).Exit(i) \/ [x!=i]emp))^* */
{
  [x=-1] 
  deadline (event["Update"(i)]{x := i}, d1);
  delay (d2);
  if (x=i) {
    event["Critical"(i)]{ct := ct +1};
    event["Exit"(i)]{ct := ct-1; x := -1};
    process (i);
  } else {
    process (i);
}
